Report on Late Winter2013 Production: Image Differencing

### 2013-03-28 W13report.tex
Readdressing convlusions.

\item An empirical computation of the variance from the image plane,
  compared to the median propagated variance in the variance plane,
  indicates that we consistently underestimate the variance by $1-2\%$
  (Table~\ref{tab-variance1}).  A proper tracking of covariance during
  the multiple image convolutions that occur may alleviate this
  problem.

\item When convolving to PSF--match, variance planes of postfiltered
  detection images have {\it lower} variance than their prefiltered
  counterparts by $2-3\%$ (Table~\ref{tab-variance2}).  These images
  have gone through one additional convolution compared to the
  prefiltered data.

@@

\item Several statistics that we are able to calculate at the time of
  image subtraction are shown to correlate strongly with the numbers
  of false detections, providing real--time quality estimates
  (Figures~\ref{}).

\item The numbers of false detections that associate with Sources is
  shown to correlate with the amount of smoothing that occurs in the
  PSF matching, in the sense that more smoothing leads to fewer false
  detections (Figure~\ref{}).  In this sense, there is a strong
  preference for running in prefiltered mode.

@@

>>>>

\item An empirical computation of the variance from the image plane,
  compared to the median propagated variance in the variance plane,
  indicates that we consistently underestimate the variance in
  prefiltering by $1-2\%$, and in postfiltering by $4-5\%$ when not
  strongly deconvolving (Table~\ref{tab-variance1}).  The latter
  effect is shown to arise from the PSF--filtering of the difference
  image immediately before detection.  This is likely due to the
  double--convolution that is happening to the template image, and our
  having no current mechanism to track pixel covariance.

\item The empirical variance of the detection images in prefiltering
  and postfiltering are similar to within $1\%$
  (Table~\ref{tab-variance2}).  However, the variance in the
  postfiltered data is $3-4\%$ {\it lower} in the postfiltered data,
  leading to a larger number of false positives when using the
  variance plane as the definition of sigma.

@@

\item The measurement of {\tt DiaSources} detected at 5--sigma are
  shown to have a commensurate measured signal--to--noise
  (Figure~\ref{fluxerr}).

@@

\item Several statistics that we are able to calculate at the time of
  image subtraction are shown to correlate strongly with the numbers
  of false detections (Figure~\ref{corrpost} and
  Figure~\ref{corrpre}).  However, these relationships have a shallow
  slope in the area of interest (number of false detections per sensor
  less than 10).  Additional work will be required to produce a robust
  predictor of false positive rate.
